Evaluating the Capabilities of Lattice Boltzmann Method for non-Newtonian and Free-surface Flows towards Applications in Wellbore Cementing

### 2016-07-19 thesis.tex
added algorithm package and fancyref prefix
editted acknowledgements

%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage[plain]{fancyref}
\usepackage{tabulary}
\usepackage{pbox}

@@

\preface
I would like to thank my wife and best friend, Shelby, my parents, and my family.
Without their love, support, and example, I would have nothing.
I would like to thank my advisor, Dr. John Brigham, for his patience and for all that he has taught me. 
I would also like to thank the other members of my committee, Dr. Julie Vandenbossche, and Dr. Anthony Iannacchione, whom have both been great guides and teachers to me.
Lastly, I would like to thank my fellow students for helping me along the way to learn and for the comradery that every graduate student needs.

>>>>

%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage[plain]{fancyref}
\usepackage{tabulary}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\def\mkfancyprefix#1#2{%
  \@namedef{fancyref#1labelprefix}{#1}%
  \begingroup\def\x{\endgroup\frefformat{plain}}%
    \expandafter\x\csname fancyref#1labelprefix\endcsname
      {\MakeLowercase{#2}\fancyrefdefaultspacing##1}%
  \begingroup\def\x{\endgroup\Frefformat{plain}}%
    \expandafter\x\csname fancyref#1labelprefix\endcsname
      {#2\fancyrefdefaultspacing##1}%
}
\makeatother
\mkfancyprefix{algo}{Algorithm}

@@

\preface
I would like to thank my wife and best friend, Shelby, my parents, and my family.
Without their love, support, and example, I would have nothing.
I would like to thank the best advisor ever, Dr. John Brigham, for his patience and for all that he has taught me. 
I would also like to thank the other members of my committee, Dr. Julie Vandenbossche, and Dr. Anthony Iannacchione, whom have both been great guides and teachers to me.
Lastly, I would like to thank my fellow students, especially Rob, Jing, Mo, and Scott, for helping me to learn along the way and for the comradery that every graduate student needs.
